---
title: "Documentation"
output: html_document
date: "2023-11-02"
---

# Introduction

This document provides documentation for the `transform_data_dev` function.

# Function Usage

The `transform_data_dev` function allows you to calculate either the average or total income for each age group.

## Calculate Average Income

```{r}
source("Exercise1.R")
```

To calculate the average income for each age group, use the following:

```{r}
library(dplyr)  # for data manipulation

# Load the sample data from a CSV file
data <- read.csv("Exercise1_data.csv")

# Calculate average income
result <- transform_data_dev(data, calc_method = "average")
result
```

## Calculate Total Income

To calculate the total income for each age group, use the following:

```{R}
library(dplyr)  # for data manipulation

# Load the sample data from a CSV file
data <- read.csv("Exercise1_data.csv")

# Calculate total income
result <- transform_data_dev(data, calc_method = "total")
result
```

## Conclusion

This function provides flexibility in calculating income statistics based on the chosen method.
