---
title: "Documentation"
output: html_document
date: "2023-11-02"
---

```{r setup, include=FALSE} 
# this chunk contains code that sets global options for the entire .Rmd. 
# we use include=FALSE to suppress it from the top of the document, but it will still appear in the appendix. 

knitr::opts_chunk$set(echo = FALSE) # actually set the global chunk options. 
# we set echo=FALSE to suppress code such that it by default does not appear throughout the document. 
# note: this is different from .Rmd default
```

# Introduction

This document provides documentation for the `transform_data_dev` function.

# Function Usage

The `transform_data_dev` function allows you to calculate either the average or total income for each age group.

## Calculate Average Income

```{r}
source("Exercise1.R")
```

To calculate the average income for each age group, use the following:

```{r}
library(dplyr)  # for data manipulation
library(readr)

# Load the sample data from a CSV file
data <- read_csv("Exercise1_data.csv")

# Calculate average income
result <- transform_data_dev(data, calc_method = "average")
result
```

## Calculate Total Income

To calculate the total income for each age group, use the following:

```{R}
library(dplyr)  # for data manipulation

# Load the sample data from a CSV file
data <- read.csv("Exercise1_data.csv")

# Calculate total income
result <- transform_data_dev(data, calc_method = "total")
result
```

## Conclusion

This function provides flexibility in calculating income statistics based on the chosen method.

## Appendix: All code in this assignment

```{r ref.label=knitr::all_labels(), echo=TRUE, eval=FALSE} 
# this chunk generates the complete code appendix. 
# eval=FALSE tells R not to run (``evaluate'') the code here (it was already run before).
```
